---
title: "Untitled"
author: "Maggie Christman"
date: "11/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Read and Clean Data

```{r, warning = F, message = F}
library(dplyr)
library(tidyr)
```

```{r}

catch_original <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/df35b.302.1", 
                               method = "libcurl"),
                               stringsAsFactors = FALSE)
head(catch_original)
```

Remove `all` column and `notes` column because we don't need them.

```{r}
catch_data <- catch_original %>% 
  # select(Region, Year, Chinook, Sockeye, Coho, Pink, Chum)
  select(-All, -notesRegCode)

head(catch_data)
```

```{r}
summary(catch_data)
```

## Fix Chinook Column

Use `mutate` to fix Chinook column

```{r}
catch_clean <- catch_data %>% 
  mutate(Chinook = ifelse(Chinook == "I", 1, Chinook)) %>%  
  mutate(Chinook = as.numeric(Chinook))
```
Finding the rows that got turned into NA

```{r}
i <-  which(is.na(catch_clean$Chinook))
i
```

```{r}
catch_original[i, ]
```


# Reshape Data

```{r}
catch_long <-  catch_clean %>% 
  pivot_longer(cols = -c(Region, Year),
               names_to = "Species",
               values_to = "Count")
head(catch_long)
```

```{r}
catch_wide <- catch_long %>% 
  pivot_wider(names_from = Year,
              values_from = Count)
head(catch_wide)
```

`rename` count colum to `catch_thousands`

```{r}
catch_long <- catch_long %>% 
  rename(catch_thousands = Count)

head(catch_long)
```

```{r}
catch_long <- catch_long %>% 
  mutate(catch = catch_thousands * 1000) %>% 
  select(-catch_thousands)

head(catch_long)
```


# Summarize Data

```{r}
mean_region <- catch_long %>% 
  group_by(Region, Species) %>% 
  summarize(catch_mean = mean(catch),
            num_obs = n())

mean_region
```

Calculate total catch per species

```{r}
total_catch <- catch_long %>% 
  group_by(Species) %>% 
  summarize(total_catch = sum(catch),
            num_obs = n()) %>% 
  arrange(desc(total_catch))

total_catch
```

```{r}
total_species_pre_1900 <- catch_long %>% 
  filter(Year < 1900) %>% 
  group_by(Species) %>% 
  summarise(total = sum(catch)) %>% 
  arrange(desc(total))

total_species_pre_1900
```

# Join to Region Table

Read in reagion data table

```{r}
region_defs <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/df35b.303.1", 
                        method = "libcurl"),
                        stringsAsFactors = F) %>% 
  select(code, mgmtArea)

head(region_defs)
```

```{r}
catch_joined <- left_join(catch_long, region_defs, by = c("Region"= "code"))

head(catch_joined)
```

# Separate and Unite

```{r}
site_codes <- data.frame(site = c("HAW-100",
                                  "HAW-101",
                                  "OAH-102",
                                  "OAH-103",
                                  "MAI-100"),
                         stringsAsFactors = F)
```

Separate island and site number using 'separate'

```{r}
site_codes_split <- site_codes %>% 
  separate(site, into = c("island", "site_num"), sep = "-", remove = F)

site_codes_split
```
```{r}
united <- site_codes_split %>% 
  unite(col = site_code, island, site_num, sep = "_", remove = F)

united
```

